Naming Anonymous JavaScript Functions

### 2011-04-07 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
section 4 reorganized. tree walk algorithm pseudo code is added.

%In this paper, we analyze function creation and consumption in ten famous project. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.

%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.

@@

\begin{figure}[htp]
%{\small 
%\begin{verbatim}

\lstset{basicstyle=\scriptsize}
\lstset{emph={FOO,BAR},emphstyle=\textit}
%\lstset{backgroundcolor=\color{yellow}}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {         // main<
10   return function() {           // main
11     var foo = new FOO("a");
12     var bar = new BAR("b");
13     var result = op(
14       function(value){          // main/result<
15         return value;
16        });
17   }
18 }();
19 var FOO = function(a) {         // FOO
20   this.a = a;
21 }
22 var BAR = function(b) {         // BAR
23   this.b = b;
24 }
25 var op = function() {           // op<
26   var local;
27   return function(callBack) {   // op
28     local++;
29     return callBack(local);
30   }
31 }();
\end{lstlisting}
%\end{verbatim}}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

@@

%\subsection{Is it possible to automatically name functions?}
%\subsubsection{Static vs. Dynamic}
% Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?

%\subsubsection{Local vs. Global}
%the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.

%\subsubsection{Is it possible to automatically name all functions?}

%\subsubsection{Other Challenges}%
% functions pass the name as string, different types of class definitions

@@

Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code.
By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree. For each function body, we walk up the tree looking for the constructs in table 2. As we describe in section XX, for every matching construct we record identifiers or expressions to use in constructing a name. 
Then we assemble a name using the expression-reduction rules outlined in section YY and the context naming rules in section ZZ. The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens. It compactly explains the function object creation, consumption and assignment. For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.

%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
%  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyze the source code and build a summary that explains the function object creation, consumption and assignment.
This summary which only contains identifiers (i.e., variable and property names) and strings available in the source code gives us the ingeredients for function identifier construction.

  %We analyze the source code to obtain the alias(es) that used for the function object or  is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.

    %  On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created. Therefore, we analyze the code to find all names that the function object is assigned to them. For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.

@@

The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value. We can explain the function object consumption after its creation in two steps: 1) the function object is called (case 9 in table 2). 2) the result is assigned to {\small\texttt{main}} (case 6 in table 2). This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.   We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".

The function in line 10 is returned just after its creation. However, as the enclosing function is just called after its creation we can follow the function object flow in the enclosing scope and see that the function object is assigned to {\small\texttt{main}}. The summary of the function object consumption will be: 1) the function object is returned (case 10, table 2), 2) the function object is assigned to {\small\texttt{main}} (case 6 table 2). As the function object is directly assigned to this variable we name the function {\small\texttt{main}}. BUT I DON"T GET IT.

The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} . Here 1) the function object is passed as an argument to function {\small\texttt{op}} (case 11), 2) The call result is assigned to {\small\texttt{result}} (case 6). If we simply put of identifiers in this summary together we get {\small\texttt{main/result<op()}}. The first part before slash  shows the context name (the enclosing function name) for this function.  However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object. Therefore, as we explain in the next subsection, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary. After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}. Eliding identifiers is important to avoid creating long, unwieldy names.

@@

\begin{table}
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline 
   1 &
   & 
   &  
   & direct access.
   & bar\textsuperscript{*}.foo = function()\{...\}\\
   \cline{0-0}\cline{5-6}

   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
   & 
   & 
   & \raggedright hashmap access by a string. 
   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   3 &
   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
   & \raggedright hashmap access by a variable name.
   & bar\textsuperscript{*}[foo] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   4 &
   & 
   & 
   & \raggedright hashmap access by a JavaScript expression.
   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
   \cline{0-0}\cline{5-6}

   5 &
   &
   &
   & \raggedright  array index.
   & foo\textsuperscript{*}[0] = function()\{...\} \\
   \cline{0-0}\cline{4-6}

   6 &
   & 
   & \multicolumn{2}{|l|}{
      variable.}
   & foo = function()\{...\} \\
   \cline{0-0}\cline{4-6}

   7 &
   &  
   & \multicolumn{2}{|m{2.8cm}|}{
     \raggedright property of a new object in an object literal.}
   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
   \cline{0-0}\cline{4-6}

	 8 &
	 & 
	 & \multicolumn{2}{|m{2.8cm}|}{
	   new array index in an array literal.} 
   & [..., function()\{...\}, ...] \\ 
   \cline{0-0}\cline{3-6}

   9 &
   & \multicolumn{3}{|m{3.8cm}|}{
     \raggedright directly called.}
   & function()\{...\}() \\
   \cline{0-0}\cline{3-6}

   10 &
   & \multicolumn{3}{|m{3.5cm}|}{
     \raggedright returned from a function call.}
   & \{... return function()\{...\}\} \\
   \cline{0-0}\cline{3-6}

   11 &
   & \multicolumn{3}{|m{3.5cm}|}{
     \raggedright passed as an argument to a function.}
   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
   \hline

  \end{tabular}
  }
\caption{Different cases of function object creation and usage in JavaScript.  Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
\label{table:function-types} 
\end{table}

\subsection{Overview of the Function Object Consumption Algorithm}
Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.  Each function body results in a list of identifers and expressions marked with the kind of parse node that contributed them (\ref{sec:nodewalk}).  Some of the items on the list are dropped if their neighboring items already give better information for the name.  Then the expressions are converted to pseudo-identifiers (\ref{sec:general-element-naming}). Finally the attributes are converted to augmenting symbols on the identifiers while  the list is collapsed to a name\ref{sec:concatenate}.

\subsection{Full Function Object Consumption Name}
\label{sec:nodewalk}
The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree. For each function body we look for the path of the function object from creation to consumption. We process the abstract syntax tree from the function body node back to the root node in the enclosed function. On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}. As we go upward in the tree, we keep identifiers and whether the object consumed is the result object (rows 1-6), part of the result object (rows 7-8), or contribute to the result object (rows 9-11). Once the summary is ready we construct the identifier. The identifiers come from function calls (case 11) are ignored if there is any other type of identifier. Otherwise, only the closest function call identifier will be used. Nodes which are not one of the type specified in Table~\ref{table:function-types} are ignored.

@@

@@

\subsection{Reducing a JavaScript Expression to a Name}
\label{sec:general-element-naming}
In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
 a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT.

@@

\subsection{Building a String from Arguments}
WHAT?

@@

\subsection{Temporary Variables} %aliases for the same object

@@

\begin{figure}[htp]
\begin{verbatim}
(a)
 foo();
(b)
 foo.bar();
(c)
 foo.apply(bar, args);
(d)
 foo.call();
\end{verbatim}
\caption{Different cases of function object creation.}
\label{fig:functionCall}
\end{figure}

@@

\subsection{Object Creation}

@@

%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
%commonjs requriejs, ...
%the function name not very long like google chrome  xxxx.yyy.zzz
\subsection{Limitations}
%some long names
%"this" in names

% open problems: naming scripts loaded and evaluated by eval,
\section{Related Work}
% ecoop 2009 paper
% typing system papers

@@

%Developers usually understand JavaScript code by examining the running program in debuggers. At runtime, concrete values are available and the developer can directly check and understand object structures and control flows. Understanding a concrete value, particularly for non-primitive values such as objects and functions, is not always straightforward. To facilitate understanding these complex values in the first place, debuggers show a summary of these objects. For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful. It works like a class name in class-based languages and suggests the object structure.
\section{Conclusion}
We highlighted the problem of nameless functions in JavaScript. We studied 10 famous JavaScript projects source code. From
our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
values and functions in the call-stack.

@@

>>>>

%In this paper, we analyze function creation and consumption in ten famous project. We propose an automated approach based on extracted data from the source code for naming JavaScript functions. The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments. 
%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.

@@

\begin{figure}[htp]

\lstset{basicstyle=\scriptsize}
\lstset{emph={FOO,BAR},emphstyle=\textit}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {         // main<
10   return function() {           // main
11     var foo = new FOO("a");
12     var bar = new BAR("b");
13     var result = op(
14       function(value){          // main/result<
15         return value;
16        });
17   }
18 }();
19 var FOO = function(a) {         // FOO
20   this.a = a;
21 }
22 var BAR = function(b) {         // BAR
23   this.b = b;
24 }
25 var op = function() {           // op<
26   var local;
27   return function(callBack) {   // op
28     local++;
29     return callBack(local);
30   }
31 }();
\end{lstlisting}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

@@

%\subsection{Is it possible to automatically name functions?}
%\subsubsection{Static vs. Dynamic}
% Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?
%\subsubsection{Local vs. Global}
%the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime. 
%\subsubsection{Is it possible to automatically name all functions?}
%\subsubsection{Other Challenges}%
% functions pass the name as string, different types of class definitions

@@

Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code. By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree. For each function body, we walk up the tree recording identifiers or expressions explains the function object consumption. The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree. %Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary. Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings. After the refinment step, 
Then, we rank collected identifiers and strings and elide less relevant data from the summary. At the end we construct a string from the consumption summary. The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens. It compactly explains the function object creation, consumption and assignment. For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.

The name is built by the above process does not contain any information about enclosing scopes. We call it \textit{local name}. We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.

%To name a expression, we walk up the tree looking for the constructs in table 2. As we describe in section XX, for every matching construct we record identifiers or expressions to use in constructing a name. Then we assemble a name using the expression-reduction rules outlined in section YY and the context naming rules in section ZZ. The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens. It compactly explains the function object creation, consumption and assignment. For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.

%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
%  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyze the source code and build a summary that explains the function object creation, consumption and assignment.
%This summary which only contains identifiers (i.e., variable and property names) and strings available in the source code gives us the ingeredients for function identifier construction.
 %We analyze the source code to obtain the alias(es) that used for the function object or  is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier. 
 %  On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created. Therefore, we analyze the code to find all names that the function object is assigned to them. For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.

@@

The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value. We can explain the function object consumption after its creation in two steps: 1) the function object is called. 2) the result is assigned to {\small\texttt{main}}. This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.   We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".

The function in line 10 is returned just after its creation. This function is located inside a closure function (i.e., a function which is called directly after its creation). This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the clousre call result ({\small\texttt{main}}). The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}. As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.

The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} . Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}. If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}. The first part before slash  shows the context name (the enclosing function name) for this function.  However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object. Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary. After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}. Eliding identifiers is important to avoid creating long, unwieldy names.

@@

\begin{table}
\centering
%\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

   1 & 
   & \raggedright property of a new object in an object literal.
   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
   \cline{0-0}\cline{3-4}

	 2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
	 & \raggedright 
	   new array index in an array literal.
   & [..., function()\{...\}, ...] \\ 
   \cline{0-0}\cline{3-4}

   3 &
   & 
     \raggedright passed as an argument to a function.
   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
   \cline{0-0}\cline{3-4}

   4 &
   & \raggedright assigned to a variable or write pointer.
   & foo\textsuperscript{*} = function()\{...\} \\
   \cline{0-0}\cline{2-4}

  \end{tabular}
%  }
\caption{Different cases of function object creation and usage in JavaScript.  Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
\label{table:function-types} 
\end{table}

%\subsection{Full Function Object Consumption Name}
\subsection{Expression Value Consumption Summary}
\label{sec:nodewalk}
The algorithm builds a consumption summary for an expression, starting from the expression node walking up in the absstract syntax tree. In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}}), it calculates the consumption summary for the function. The first node is an expression and returns a value. The algorithm ends when we reach a node which is an assignment or a statmement which does not return any value. When we move from a node to its parent, the value of the node expression can be the same, part of or different from its parent expression value. For every visited node we keep this information.

\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\begin{algorithm}                      % enter the algorithm environment
\caption{Compute Object Consumption Summary for Node $n$}          % give the algorithm a caption
\label{alg1}                           % and a label for \ref{} commands later in the document
\begin{algorithmic}                    % enter the algorithmic environment
\REQUIRE Node $n$ in Abstract Syntax Tree
\ENSURE Object Consumption Summary 
\STATE $List$ $summary$ = $new$ $List$()

\WHILE {$n.parent$ is an expression}  
	\STATE $dataItem$ = $new$ $DataItem$()
    \IF {$n$ value is the same as $n.parent$ value}
    	 \STATE $dataItem.isTheSame$ = $true$
    \ELSIF {$n$ value is a property of $n.parent$ value}
    		\STATE $dataItem.isPartOf$ = $true$
    \ELSE	
	   		\STATE $dataItem.isContributedTo$ = $true$
    \ENDIF
    \IF {$n.parent$ is a function call and $n$ is an argument}
   	    \STATE $dataItem.isFunctionCall$ = $true$
   	    \STATE $dataItem.id$ = $idForFC(n.parent)$
   	    \STATE $dataItem.hint$ = $hintForFC(n.parent)$
   	\ELSIF {$n.parent$ is an object literal and $n$ is assigned to $foo$}
   	    \STATE $dataItem.isObjLiteral$ = $true$
   	    \STATE $dataItem.id$ = $foo$
    \ENDIF     
   \STATE $summary.add(dataItem)$
   \STATE $n$ = $n.parent$
\ENDWHILE

  \IF {$n.parent$ is an assignment} 
  	\STATE $dataItem$ = $new$ $DataItem$()
		\STATE $dataItem.isAssignment$ = $true$
    \STATE $dataItem.id$ = $idForAssignment(n.parent)$
    \STATE $summary.add(dataItem)$
  \ENDIF	
  \RETURN $summary$
\end{algorithmic}
\end{algorithm}

Once we move from a node to its parent, we keep the

%The algorithm build a consumption summary for an expression which returns a value. A consumption summary is a list of collected information at every not in the tree traversal. At every node two items are stored. First the relation of the consumed value and the result value. The consumed expressions can be part of the result expression like first two cases in table 2. The result value might be different from the consumed value like case 3 in table 2. Morover we keep identifiers at every node is one of the constructs in table 2.

%Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.  Each function body results in a list of identifers and expressions marked with the kind of parse node that contributed them (\ref{sec:nodewalk}).  Some of the items on the list are dropped if their neighboring items already give better information for the name.  Then the expressions are converted to pseudo-identifiers (\ref{sec:general-element-naming}). Finally the attributes are converted to augmenting symbols on the identifiers while  the list is collapsed to a name\ref{sec:concatenate}.

The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree. For each function body we look for the path of the function object from creation to consumption. We process the abstract syntax tree from the function body node back to the root node in the enclosed function. On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}. As we go upward in the tree, we keep identifiers and whether the object consumed is the result object (rows 1-6), part of the result object (rows 7-8), or contribute to the result object (rows 9-11). Once the summary is ready we construct the identifier. The identifiers come from function calls (case 11) are ignored if there is any other type of identifier. Otherwise, only the closest function call identifier will be used. Nodes which are not one of the type specified in Table~\ref{table:function-types} are ignored.

@@

%\subsection{Variable Refinement}\subsubsection{Read Variable}\subsubsection{Write Variable}

%\subsection{Temporary Variables} %aliases for the same object

\subsection{Expression Reductions}
\subsubsection{to a Name}
\label{sec:general-element-naming}
In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
 a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT. 
\subsubsection{to a Hashmap Key}

\subsubsection{Building a String from Arguments}
WHAT?

@@

@@

\subsection{Enclosed By a Closure Function}
A closure function is called directly after its creation. Therefore a closure function is like a simple block and any static analysis like
for buiilding object consumption summary and variable refinement can be continued outside a closure function. Every expression which its value
is returned in the closure function is assigned to the expression that closure function call result is assigned to. Morover, in cases where the
function call defines "this" (by apply()) or arguments these variables can be replaced in the function body.

@@

@@

@@

@@

%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
%commonjs requriejs, ...
%the function name not very long like google chrome  xxxx.yyy.zzz

\section{Disucussion}

\subsection{Limitations}
%some long names
%"this" in names

% open problems: naming scripts loaded and evaluated by eval,
\section{Related Work}
% Andrew Ko paper about errors by names
% ecoop 2009 paper
% typing system papers

@@

%Developers usually understand JavaScript code by examining the running program in debuggers. At runtime, concrete values are available and the developer can directly check and understand object structures and control flows. Understanding a concrete value, particularly for non-primitive values such as objects and functions, is not always straightforward. To facilitate understanding these complex values in the first place, debuggers show a summary of these objects. For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful. It works like a class name in class-based languages and suggests the object structure.

\section{Conclusion}
We highlighted the problem of anonymous functions in JavaScript. We studied 10 famous JavaScript projects source code. From
our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
values and functions in the call-stack.

@@

\section{To Be Removed}
